---
title: "Lists - In Class Exercises"
author: "Viviana Larar"
date: "DATA 2401"
output:nhtml_document

---

# Exercises: 

Make a list that contains the information on a single playing card. Suit, face, and value. 

```{r}
playing_card <- list(
  suit = "heart",
  face = "queen",
  value = 12,
)

```


Make a second list where each element contains all the options for suit, face, and value, respectively. 

```{r}
playing_card <- list(
  suit = c("heart", "spade", "diamond", "club"),
  face = c("king", "queen", "jack"),
  value = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 10, 10)
)

```


If `Newlist <- list(a=1:10, b="Good morning", c="Hi")`, write an R statement that will add 1 to each element of the first vector in Newlist.

```{r}
Newlist <- list(a=1:10, b="Good morning", c="Hi")

Newlist[[1]] + 1
```

If `b <- list(a=1:10, c="Hello", d="AA")`, write an R expression that will give all elements of the first vector of b, except the second, and write another that returns only elements of `a` that are greater than 7.

```{r}
b <- list(a=1:10, c="Hello", d="AA")

# gives first and third element
b$c <- NULL
str(b)

# returns only elements of a greater than 7
b$a[b$a > 7]

# same but also kinda the worst
b[[1]][b[["a"]] > 7]

```

Let `x <- list(a=5:10, c="Hello", d="AA")`, write an R statement to add a new item z = "NewItem" to the list x.

```{r}
x <- list(a=5:10, c="Hello", d="AA")
x$z <- "NewItem"
print(x)
```
